Model

### 2019-08-25 stats/model.Rmd
add third model run

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
    slope: uniformDrift({a: 0, b: 3, width: 0.5})
  }

@@

# load this for model parameters
sem_know_model <- readRDS("../saves/sem_know_new_model.rds")#%>%

# load this for model parameters with wider prior on so_slope
#saveRDS(sem_know_model, "../saves/sem_know_new_model_2.rds")

>>>>

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
    slope: uniformDrift({a: 0, b: 2, width: 0.5})
  }

@@

# load this for model parameters
sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# load this for model parameters with wider prior on so_slope (0:3)
#sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")

# load this for model parameters with even wider prior on so_slope (0:4)
#sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

#saveRDS(sem_know_model, "../saves/sem_know_new_model_3.rds")
